A Large-scale Study of Polymorphism in R

### 2019-03-18 paper/main.tex
few type examples

\begin{figure}{\small
\begin{lstlisting}[style=R]
> normSum <- function( m )  round( m / sum(m), 2)
> normSum(c(1L,3L,6L))
[1] 0.1 0.3 0.6
> normSum(c(1.1,3.3,6.6))
[1] 0.1 0.3 0.6
> normSum(c(1.6,3.3,6.1))
[1] 0.15 0.30 0.55
> normSum(complex(r=rnorm(3),i=rnorm(3))
[1] 0.49+0.21i 0.30-0.18i 0.22-0.03i
\end{lstlisting}}
\caption{Sample R code}\label{sample}
\end{figure}

@@

%% TODO : make the types all bold.

attributes:

>>>>

\begin{figure}{\small
\begin{lstlisting}[style=R]
> normSum <- function( m )  round( m / sum(m), 2)
> normSum(c(1L,3L,6L))
[1] 0.1 0.3 0.6
> normSum(c(1.1,3.3,6.6))
[1] 0.1 0.3 0.6
> normSum(c(1.6,3.3,6.1))
[1] 0.15 0.30 0.55
> normSum(complex(r=rnorm(3),i=rnorm(3)))
[1] 0.49+0.21i 0.30-0.18i 0.22-0.03i
\end{lstlisting}}
\caption{Sample R code}\label{sample}
\end{figure}

@@

%% TODO : make the types all bold.
\AT{Some examples of use of \code{typeof}:}
To build a sense of how these types arise in R code, consider the following:
\AT{We could think of another way to do this also.}

	\item \code{typeof(5) == typeof(c(5)) == typeof(c(5, 5)) == "double"}.
	As we mentioned, R is vectorized, so even apparent scalars are vectors.
	\AT{Just for fun,} note that \code{5[1] == 5} in R.

	\item to actually get an integer, you need \code{typeof(5L) == "integer"}.
	Doubles are by far the most common numeric type in R \AT{I can get data for this}, and you can even use them to index lists and vectors: \code{list(1, 2)\[\[1.9\]\] == 1}.
	Note the double brackets for list indexing.

	\item NAs are common in data-centric languages (e.g. MATLAB, \AT{others?}), and R is no exception.
	As for their type, we see that \code{typeof(NA) == "logical"}, but that isn't to say that NA only has type logical.
	Consider \code{typeof(c(1, NA, 3)\[2\])}: NA actually inhabits every type in R, \AT{details}.

	\item \AT{other examples?}

Another form of type information relates to metadata on values, and R allows programmers to add said metadata in the form of {\it attributes}.
The functionality to do so in R is through the \code{attributes(x)} and \code{attr(x, "name")}  functions.
\code{attributes}
